Verifying Demonstrations

### 2018-05-30 paper/LocationProofs.tex

One possible way to counter this threat is by having the requesting device formally proven that it really is at the claimed location, which give rise to the concept of \emph{location proof}. 
In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time. A location proof architecture is a system by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof.
\seb{add references to location proof systems} 
Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
However, some location proofs systems, such as PROPS \cite{DBLP:conf/srds/GambsKRT14}, exists that provides strong privacy guarantees along with the possibility of verifying the claim of the location. 
\PRIVO share some similarities with PROPS, although their objective is quite different as it aims at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made by a user, which is an individual property.

>>>>

One possible way to counter this threat is by having the requesting device formally proven that it really is at the claimed location, which give rise to the concept of \emph{location proof}. 
In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time. A location proof architecture is a system by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof.
\seb{add references to location proof systems} 
Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
However, some location proofs systems, such as PROPS~\cite{PROPS}, exists that 
provides strong privacy guarantees along with the possibility of verifying the 
claim of the location. \PRIVO share some similarities with PROPS, although 
their objective is quite different as it aims at verifying a global property of 
the population (\ie crowd estimation) in contrast to checking the location 
claim made by a user, which is an individual property.
